Reproducible Research Peer Assessment 1
========================================================
Douwe Krooshof

## Loading the data file
Note: I assume the activity.csv to be present in the working directory!

```{r echo=TRUE}
setwd("C:/Users/dkrooshof/Desktop/Coursera/Steps")
steps <- read.csv("activity.csv",header=TRUE)
```

I also convert the dates from string to date format:

```{r echo=TRUE}
steps$date <- as.Date(steps$date,format='%Y-%m-%d')
```

## Making the histogram:
- First I aggregate the samples per day
- Then I make a histogram with ggplot2

```{r echo=TRUE}
StepsPerDay <- aggregate(steps ~ date, data=steps, FUN=sum)
library(ggplot2)
qplot(steps, data=StepsPerDay, geom="histogram",binwidth=5000)
```

## Mean and median steps per day:
I take the mean and median function with the na.rm option:
```{r echo=TRUE}
mean(StepsPerDay$steps, na.rm=TRUE)
median(StepsPerDay$steps, na.rm=TRUE)
```

## Daily activity patttern:
I use the aggregate function again on the original data, now to take the mean per interval number rather than aggregate per day:
```{r echo=TRUE}
StepsPerInterval <- aggregate(steps ~ interval, data=steps, FUN=mean)
```

Then, I make a line plot with the interval number on the x-axis and the mean number of steps per interval on the y-axis:
```{r echo=TRUE}
qplot(interval,steps,data=StepsPerInterval,geom="line")
```

The interval with the maximum mean number of steps per interval was found in the following way (835):
```{r echo=TRUE}
StepsPerInterval[which.max(StepsPerInterval[,2]),1]
```

## Inputing missing values
I decided to input missing values by assigning a missing value the mean of the interval number. I have got got thi to work yet (sorry!)

```{r echo=TRUE}
StepsAdjusted <- merge(steps,StepsPerInterval,by.x="interval",by.y="interval")
StepsAdjusted$missing = is.na(StepsAdjusted$steps.x)


for (i in StepsAdjusted$){
    if(StepsAdjusted[i,5] == TRUE){
       StepsAdjusted[i,6] <-  StepsAdjusted[i,4]
    }else{
        StepsAdjusted[i,6] <-  StepsAdjusted[i,2]
    }
}

```



